### 2016-04-10 Chapters/chap4/chap4.tex
Improve fig, revision

Weinstein {\em et al.} designed and investigated three donor–bridge–acceptor (DBA) molecular triads \cite{delor2014toward,delor2015mechanism,scattergood2014electron}: PTZ-CH\textsubscript{2}-Ph-C$\equiv$C-Pt- C$\equiv$C-NAP, PTZ-Ph-C$\equiv$C-Pt- C$\equiv$C-NAP and OMe-PTZ-Ph-C$\equiv$C-Pt- C$\equiv$C-NAP (D = PTZ is phenothiazine and A = NAP is naphthalene-monoimide, see Fig. \ref{JuliaStruct}(a)). From now on, they are further abbreviated as PTZ-CH\textsubscript{2}-Pt-NAP, PTZ-Pt-NAP and OMe-PTZ-CH\textsubscript{2}-Pt-NAP, respectively.

@@

\begin{figure*}[!t]
\includegraphics[width=\columnwidth]{Chapters/chap4/Images/molecules.jpg}
\caption{\textbf{a}. Molecular structure of PTZ-CH\textsubscript{2}-Pt-NAP, PTZ-Pt-NAP and OMe-PTZ-CH\textsubscript{2}-Pt-NAP, from left to right. \textbf{b}. Energy level diagrams for the ET process, with the free energy driving force of charge separation ($\Delta$G) indicated. Adapted with permission from Ref.~\cite{delor2015mechanism}.\label{JuliaStruct}}
\end{figure*}

@@

@@

@@

\begin{figure}[!t]
\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap4/Images/plmT12.png}}\\
\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap4/Images/plmT13.png}}
% \subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap4/Images/plmT31.png}}\\
% \subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap4/Images/plmT32.png}}
\caption{
Projection of primary mode of (a) CSS $\rightarrow$ \textsuperscript{3}NAP, (b) CT $\rightarrow$ \textsuperscript{3}NAP calculated at \textsuperscript{3}NAP geometry onto the normal modes of \textsuperscript{3}NAP. Embedded molecule shows the atomic displacement vectors of primary mode.}\label{projT1}
\end{figure}

\begin{figure}[!h]
% \subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap4/Images/plmT12.png}}\\
% \subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap4/Images/plmT13.png}}
\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap4/Images/plmT31.png}}\\
\subfloat[]{\includegraphics[width=0.95\columnwidth]{Chapters/chap4/Images/plmT32.png}}
\caption{
Projection of primary mode of (a) CT $\rightarrow$ \textsuperscript{3}NAP, and (b) CT $\rightarrow$ CSS calculated at CT geometry onto the normal modes of CT. Embedded molecule shows the atomic displacement vectors of primary mode.
}\label{projT3}
\end{figure}

@@

As experiments show that the excitation of C$\equiv$C bond radically affected the ET process, we expect the triple bond vibration to dominate the primary modes, at least for the CT state based calculations, since they achieve good agreement. Fig. \ref{projT1} and \ref{projT3} show the projection of primary modes onto the normal modes of corresponding state, {\em i.~e.}, the primary modes calculated at CT geometry are projected onto the normal modes of the CT state, and those at \textsuperscript{3}NAP are projected onto \textsuperscript{3}NAP's normal modes. It turns out that all four primary modes involve obvious C$\equiv$C displacement, and it is verified by the projections. The projections of primary modes are dominated by 1 or 2 normal modes. In Fig. \ref{projT1}(a), it is the 174th normal mode (ordering by increasing frequency); in Fig. \ref{projT1}(b), the 174th and 175th modes dominate. SIilarly, it is 174th and 175th modes dominate in Fig. \ref{projT3}(a) and the 175th mode in Fig. \ref{projT3}(b). All these normal modes are C$\equiv$C stretching modes, as shown in Fig. \ref{NMT1T3}. We suggest that the primary mode of  CT $\rightarrow$ CSS transition (Fig. \ref{projT3}(b)) is the one involves C$\equiv$C vibration most. It has a component which has the largest weight, > 0.25, in all four primary modes. And that component clearly dominates other normal modes. As for PTZ-CH\textsubscript{2}-Pt-NAP, the CT $\rightarrow$ CSS step can be fully switched off by vibronic excitation, the step is supposed to be the one influenced by C$\equiv$C stretching most. Although PTZ-Pt-NAP does not show such radical change, we expect the the CT $\rightarrow$ CSS to be the most C$\equiv$C involved, as two molecules only differ by a -CH\textsubscript{2}-

@@

However, interestingly, the results at CT geometry get worse. For the CT $\rightarrow$  CSS reaction, the average diabatic coupling is so unreasonable that Eq. \ref{mixingangle} does not have any real solution, so it is absent in Fig. \ref{rateComp}. Looking at Fig. \ref{interCondon}, we suspect that the best choice of diabatic coupling is where Condon approximation holds, i.e., where the change of coupling is slow. The proposition can be tested when the calculations of other two molecules, PTZ-CH\textsubscript{2}-Pt-NAP and OMe-PTZ-CH\textsubscript{2}-Pt-NAP are complete.

>>>>

Weinstein {\em et al.} designed and investigated three donor–bridge–acceptor (DBA) molecular triads \cite{delor2014toward,delor2015mechanism,scattergood2014electron}: PTZ-CH\textsubscript{2}-Ph-C$\equiv$C-Pt- C$\equiv$C-NAP, PTZ-Ph-C$\equiv$C-Pt- C$\equiv$C-NAP and OMe-PTZ-Ph-C$\equiv$C-Pt- C$\equiv$C-NAP (D = PTZ is phenothiazine and A = NAP is naphthalene-monoimide, see Fig. \ref{JuliaStruct}(a)). From now on, they are further abbreviated as PTZ-CH\textsubscript{2}-Pt-NAP, PTZ-Pt-NAP and OMe-PTZ-Pt-NAP, respectively.

@@

\begin{figure*}[!t]
\includegraphics[width=\columnwidth]{Chapters/chap4/Images/molecules.jpg}
\caption{\textbf{a}. Molecular structure of PTZ-CH\textsubscript{2}-Pt-NAP, PTZ-Pt-NAP and OMe-PTZ-Pt-NAP, from left to right. \textbf{b}. Energy level diagrams for the ET process, with the free energy driving force of charge separation ($\Delta$G) indicated. Adapted with permission from Ref.~\cite{delor2015mechanism}.\label{JuliaStruct}}
\end{figure*}

@@

\begin{figure*}[!h]
\includegraphics[width=0.45\columnwidth]{Chapters/chap4/Images/parabola.jpg}
\caption{Calculated energies of the CT (black), CSS (blue) and 3NAP (red) states along the NAP side C$\equiv$C coordinate in the ground state geometries of the molecules studied, in CH\textsubscript{2}Cl\textsubscript{2}. a, PTZ-CH\textsubscript{2}-Pt-NAP. b, PTZ-Pt-NAP. c, OMe-PTZ-Pt-NAP. The first and second vibrational energy levels for the asymmetric C$\equiv$C stretch are shown for the CT state. The energy gaps from $\nu_0$ to the intersection between CT and CSS are shown in the insets. There is a clear trend concerning the energy gap: PTZ-CH\textsubscript{2}-Pt-NAP < PTZ-Pt-NAP < OMe-PTZ-Pt-NAP, reflecting the trend experimentally observed in the efficiency of the infrared control effect. Reprinted with permission from Ref.~\cite{delor2015mechanism}.\label{PTZparabolas}} \end{figure*}

@@

Weinstein propose the effect of infrared control relies on the distance between CT energy minimum and the intersection of CT and CSS potential energy surfaces. For all three molecules, two PESs intersect where C$\equiv$C bond is slightly longer than the equilibrium length. When C$\equiv$C bond gets excited, it elongates and helps molecules to pass the intersection. If the energy gap between intersection and equilibrium geometry is much larger than C$\equiv$C vibrational energy, the dynamics is barely affected; if the energy gap is small, the vibrational excitation can radically change the dynamics. It agrees to that PTZ-CH\textsubscript{2}-Pt-NAP has the smallest energy gap in theoretical calculations, as illustrated in Fig. \ref{PTZparabolas}.

@@

\begin{figure}[!t]
\subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT12.png}}\\
\subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT13.png}}
% \subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT31.png}}\\
% \subfloat[]{\includegraphics[width=0.88\columnwidth]{Chapters/chap4/Images/plmT32.png}}
\caption{
Projection of primary mode of (a) CSS $\rightarrow$ \textsuperscript{3}NAP, (b) CT $\rightarrow$ \textsuperscript{3}NAP calculated at \textsuperscript{3}NAP geometry onto the normal modes of \textsuperscript{3}NAP. Embedded molecule shows the atomic displacement vectors of primary mode.}\label{projT1}
\end{figure}

\begin{figure}[!h]
% \subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT12.png}}\\
% \subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT13.png}}
\subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT31.png}}\\
\subfloat[]{\includegraphics[width=0.89\columnwidth]{Chapters/chap4/Images/plmT32.png}}
\caption{
Projection of primary mode of (a) CT $\rightarrow$ \textsuperscript{3}NAP, and (b) CT $\rightarrow$ CSS calculated at CT geometry onto the normal modes of CT. Embedded molecule shows the atomic displacement vectors of primary mode.
}\label{projT3}
\end{figure}

@@

As experiments show that the excitation of C$\equiv$C bond radically affected the ET process, we expect the triple bond vibration to dominate the primary modes, at least for the CT state based calculations, since they achieve good agreement. Fig. \ref{projT1} and \ref{projT3} show the projection of primary modes onto the normal modes of corresponding state, {\em i.~e.}, the primary modes calculated at CT geometry are projected onto the normal modes of the CT state, and those at \textsuperscript{3}NAP are projected onto \textsuperscript{3}NAP's normal modes. It turns out that all four primary modes involve obvious C$\equiv$C displacement, and it is verified by the projections. The projections of primary modes are dominated by 1 or 2 normal modes. In Fig. \ref{projT1}(a), it is the 174th normal mode (ordered by increasing frequency) that dominates; in Fig. \ref{projT1}(b), the 174th and 175th modes dominate. Similarly, 174th and 175th modes dominate in Fig. \ref{projT3}(a) and  175th mode in Fig. \ref{projT3}(b). All these normal modes are C$\equiv$C stretching modes, as shown in Fig. \ref{NMT1T3}. We suggest that the primary mode of  CT $\rightarrow$ CSS transition (Fig. \ref{projT3}(b)) is the one involves C$\equiv$C vibration most. It has a component which has the largest weight, > 0.25, in all four primary modes. And that component clearly dominates other normal modes. As for PTZ-CH\textsubscript{2}-Pt-NAP, the CT $\rightarrow$ CSS step can be fully switched off by vibronic excitation, the step is supposed to be the one influenced by C$\equiv$C stretching most. Although PTZ-Pt-NAP does not show such radical change, we expect the the CT $\rightarrow$ CSS to be the most C$\equiv$C involved, as two molecules only differ by a -CH\textsubscript{2}-

@@

However, interestingly, the results at CT geometry get worse. For the CT $\rightarrow$  CSS reaction, the average diabatic coupling is so unreasonable that Eq. \ref{mixingangle} does not have any real solution for $\theta$, so it is absent in Fig. \ref{rateComp}. Looking at Fig. \ref{interCondon}, we suspect that the best choice of diabatic coupling is where Condon approximation holds, i.e., where the change of coupling is slow. The proposition can be tested when the calculations of other two molecules, PTZ-CH\textsubscript{2}-Pt-NAP and OMe-PTZ-Pt-NAP are complete.
